---
title: "FinalReport-LTER Plant Data"
author: "Vanessa Robertson-Rojas"
date: "May 23, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#needed libraries and packages
#install.packages("dplyr")
#install.packages("reader")
#install.packages("ggplot2")
#install.packages("maps")

library(dplyr)
library(readr)
library(ggplot2)
library(knitr)
library(maps)

#call data
LTERPlants<-read.csv("LTERPlants.csv")

#Make a date column
Date<-paste(LTERPlants$Year, LTERPlants$Month, LTERPlants$Day, sep="")
LTERPlants$Date <-as.Date(Date, "%Y%m%d")

#Keep relevant columns 
LTERPlants<-LTERPlants %>% select(Date, Site, Plot, Latitude, Longitude, Species_Code, Plant_Biomass, Shoot_Height)

```
#Intro
####This data was collected at the Georgia Coastal Ecosystems LTER Site on the south-central coast of Georgia, USA. Plant species and growth metrics were measured during the spring of 2000 across 8 plots. 

```{r intro}


#Make a table of avergages and standard deviation 
LTERSummary <- LTERPlants %>% group_by(Plot) %>% summarize(Biomass_Mean = mean(Plant_Biomass, na.rm=T), Biomass_StdDev = sd(Plant_Biomass, na.rm=T), ShootHeight_Mean = mean(Shoot_Height, na.rm=T), ShootHeight_StdDev = sd(Shoot_Height, na.rm=T))

kable(LTERSummary, align='c',digits=2,caption="Table 1. Averages and Standard Deviations of Plant Biomass and Shoot Height.")

```

#Methods
	A quadrat survey was conducted in October 2000 to measure the species and size distribution of plants in the permanent plots at 10 GCE LTER sampling sites. The permanent plots were subdivided into two nominal zones (creek and high marsh), and 8 quadrats were randomly placed within each zone. The species, shoot height, and flowering status was recorded individually for each plant present in each quadrat within the sampling area at the mapped latitude and longitude coordinates below. 
#
```{r, fig.cap= 'Figure 1. Shows a map of the study area in Georgia, USA.'}

#ggplot map of georgia
#make lat and long objects to use for plot

plot_lat <-31.53863
plot_lon <--81.42254
georgiamap <- ggplot() + borders("state", region="Georgia") + coord_map("gilbert") + theme_grey() + geom_point(aes(x=plot_lon, y=plot_lat))
georgiamap


```

#Results
The following figure, a boxplot series of Shoot Heights across all 10 monitoring plots shows several uniquely productive plots, # 7-9. These plots may contain plant communities or phenotypes within common species that compeete well for vertical space, and will likely compete best for light resources. The second figure demonstrates that plot 7 is also uniquely prolific in biomass production. In this setting we would expect light access through height compeitition to result in higher biomass assimilation in plot 7. 
```{r, fig.cap= 'Figure 2. Shows Shoot Height across the 8 different sample plots.'}

SHplot <- ggplot(LTERPlants, aes(group=Site, x=Plot, y=Shoot_Height)) + geom_boxplot() + ggtitle("Boxplot of Shoot Height by Plot #") + theme_bw() + scale_x_discrete(name = "Unique Monitoring Plots") + scale_y_continuous(name = "Shoot Height (cm)")
SHplot

BMplot <- ggplot(LTERPlants, aes(group=Site, x=Plot, y=Plant_Biomass)) + geom_boxplot() + ggtitle("Boxplot of Plant Biomass by Plot #") + theme_bw() + scale_x_discrete(name = "Unique Monitoring Plots") + scale_y_continuous(name = "Plant Biomass (g)")
BMplot
#Shoot Height (cm) 
#Unique Monitoring Plots (1-8)


```


